\chapter{Introduction}
%Problem
%	Autism
%Setting
%Motivation
%Structure of report

Disabled people need help and this help is nowadays given through the use of technology.
However, there are still some disabled people who are using non-technological solutions to aid their needs.
Among these people, are people suffering from the mental disability known as autism.
There are many different forms of autism though, ranging from super intelligent to be unable to speak.
A shared trait though is the inability to put themselves into the mind of others.
The result of this is that they cannot interpret emotions, causing them to have difficulties when interacting with other people in social contexts.
The main focus is to help people that are having the strongest negative effect of autism, which is primarily the ones who have trouble with speech.
Currently, folders with pictures are being used to communicate with the guardians.
These folders are very cumbersome since they can grow very large in size.
Furthermore, it can be very difficult to find the specific picture you are looking for.
This is sought to improve through technology by creating an application on a mobile device that fulfils the same functionality as the folders.
By creating this application, it is possible to have the pictures located at one place without having it grow in size.
In addition to this, it could be easier for the people to find the specific picture by creating a search function in the application.

Currently this project is an ongoing development, which is built upon the work of previous generations of students.
Therefore, the project will primarily focus on getting the current features work as intended, with potential for new functionality if there are no further improvements available to the current features.
The development is done in four SCRUM sprints detailing the process of each.