\section{Sprint Backlog}
As mentioned before, in this sprint we will add missing features and resolve bugs in the application we have been assigned to.
Some of these issues are found by the group working on the program last year, and the rest have been found by testing the functionality of the application.
The different issues found are prioritised and estimated through poker planning.
By this estimation and prioritisation, the following sprint backlog was constructed:

\begin{description}[style=nextline]
	\item[Change stroke width]
	Be able to change the stroke width for freehand drawing.
	\item[Loading pictures from camera in correct size]
	Pictures loaded into the canvas are zoomed in too much, as the picture is larger than the canvas.
	\item[Colour swap]
	The colour swap button does nothing at the moment. The fill and stroke colour should be able to be swapped by a click on the colour swap button.
	\item[Straight line colour]
	Straight lines can only be drawn as black, it should be able to be drawn with ones selected colour.
	\item[Icon changes]
     In general several icons do not represent their functionality, therefore they need to be changed.
     \item[Freehand Drawing Colour]
     An unexpected swap in the colour of the last freehand drawing when swapping colours with the colour swap button occurred and should be fixed.
	\item[Clear button]
	Implement a button in canvas to clear the canvas.
	\item[Collision detection for rotated objects]
	The collision detection only works when objects are not rotated. It needs to be changed to also work for rotated objects.
	\item[Save canvas state]
	Find a way to save the drawStack between uses. That is when switching to camera and back, or between app uses.
	\item[Record Dialogue]
	Change dialogue box for recording, as the visuals does not match the expectations of how a sound recorder works.
	\item[Scale camera pictures]
	Pictures taken with the camera should be scalable in canvas.
\end{description}