\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{rotating}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

\pagestyle{fancy}
\chead{2.1.10 - sw608f14 - Daniel S. F., Lars A, Mathias W. P. \& Søren S. A.}

\lstset{mathescape = true}
\usepackage{amsthm}
\begin{document}
\chapter*{Selfstudy 5}
\section*{Exercise 1 - 33-2}
Answered in the last selfstudy.

\section*{Exercise 2}
\subsection*{Multi-way merge sort algorithm analysis}
$log_{m}(n) = log_{1000}(900000) \approx 1.985$

So 2 iterations. 

\subsection*{How to optimise}
So the 900-way merging that we have would cost $2*\frac{900000}{1} = 1.8*10^6$.
As that is reading 1 page from each block.

Instead we could do 2-way merging.
And so we could read read $30$ elements per block at at time as $30*30 = 900$
So how many files we have is $1000/31 = 32$, we divide by $31$ as there is $1$ file for the buffer.

The cost will then be $4*(\frac{900000}{32} + \frac{900000 - \frac{900000}{32}}{10}) = 0.46*10^6$
So it is clearly cheaper than the 900-way merging.

For a 3-way merging we would instead have.
$6*(\frac{900000}{90} + \frac{900000 - \frac{900000}{90}}{10}) = 0.594*10^6$

So the fastest variant is the 2-way merging for this example.

\section*{Exercise 3 - 27-1}
\subsection*{a.}
\begin{lstlisting}
Algo(A,B,C,l,r)
   if l=r
      C[l] = A[l] + B[l]
   else
      mid = $\floor{\frac{l+r}{2}}$
      spawn Algo(A,B,C,l,mid)
      Algo(A,B,C,mid,r)
      sync
\end{lstlisting}

The work is $\Theta(n)$.

The span is $\Theta(lg(n))$

So the parallelism is $\Theta(\frac{n}{lg(n)})$

\subsection*{b.}
The work is $\Theta(n)$

The span is $\Theta(n)$

So the parallelism is $\Theta(1)$ which is bad.

\subsection*{c.}
The span is $\Theta(\frac{n}{g} + g)$

$g$ is between $1$ and $n$ and for the parallelism to be maximal, the span should be minimal. So I have to find the minimum of the function $f(g) = \frac{n}{g} + g$
which can be done by differentiation.

$\frac{\delta (\frac{n}{g} +g)}{\delta g} = 1 - \frac{n}{g^2}$

And so the minimum is where  $1 - \frac{n}{g^2} = 0 \Rightarrow g = \sqrt{n}$

That would give a parallelism of $\Theta(\frac{n}{\frac{n}{\sqrt{n}} +\sqrt{n}}) =  \Theta(\sqrt{n})$

And so we can conclude that even with the best value for $g$, it is still worse than the $a$ solution.
\end{document}