\section{Usability Test}\label{sec:usability-test}
To ensure that the customers are able to use the application to create pictograms, a usability test is performed.
Furthermore, the usability test is performed to ensure that the application is easy to learn.
The reason why the application have to be easy to learn is that the customers are not used to operate with an android tablet and they are not using computers that often.
Moreover, the customers are getting a tablet with the application installed and are therefore not told how to use the application beforehand.

To make a usability test several tasks, which makes the testees try all parts of the program, are being constructed. 
The testees then have to try to complete these tasks without help from any other.
If they are unable to complete the tasks without help, they can ask the person that are with them in the room.
Problems are then described and put into categories depending on how they are complete the tasks.
The problems are categorised into three categories which are cosmetic, serious, and critical.
Problems that are categorised as cosmetic are something that are slowing the testees down by a few seconds.
When a problem is categorised as serious is when the testees are unable to solve the problem without any help or are stuck for several seconds.
The worst type of problem is critical, this problem occurs when the testees are unable to solve the problem and the person sitting next to the testees are having to show them how to perform the task.

The usability test was performed in the end of this sprint and is therefore not solved in this sprint.
However, how to solve the main problems will be described in \chapref{sec:further-development}.

\begin{table}[h]
	\centering 
	\rowcolors{2}{gray!25}{white}
	\begin{tabular}{|c|c|c|}
		\rowcolor{gray!50}
		\hline 
		Problems & Description & Category \\ 
		\hline
		P1 & Change camera picture to black and white & Cosmetic \\ 
 
		P2 & Clear canvas & Cosmetic \\ 
 
		P3 & Drawing entities & Serious \\ 

		P4 & Move entities behind another entity & Serious \\ 
 
		P5 & Swap colors & Critical \\ 
 
		P6 & Add search word & Cosmetic \\ 
 
		P7 & Delete entity & Serious \\ 
 
		P8 & Color picker & Cosmetic \\ 
 
		P9 & Play sound & Cosmetic \\ 
		\hline 
	\end{tabular} 
	\caption{Discovered usability problems.}
	\label{tab:usability-problems}
\end{table}

\subsection*{P1 - Change Camera Picture to Black and White}
A problem occurred when the test had to take a picture of their chair in black and white.
The problem was that one of the teestees just took the picture and though that they could change the colour of the picture afterwards.
Another tester would to fast and did not read the tasks good enough and therefore forgot to pick black and white.

The reason why this is a cosmetic problem is that the first tester had some problems find out how to change the colour of the picture.
However, the second tester found the color changer right when the tester was told that it should be in black and white.

\subsection*{P2 - Clear Canvas}
When the testees had to clear the canvas, after drawing, they had problems finding the button to clear the canvas.
However, after looking around for few seconds the testees were able to locate the button, which is why the problem is only cosmetic.

\subsection*{P3 - Drawing Entities}
Drawing entities is done by swipe the screen, the start position of the swipe is then the first corner and the end of the swipe is the opposite corner, the entity is then drawn using these corners.
What the testees did when trying to draw an entity was that they pressed the screen and believed that a circle would be created.

The problem is a serious problem since this is something that the customers have to use all the time.
Furthermore, the testee also used several seconds figuring out how the problem react when drawing an entity.
However, none of the testee needed help to be able to draw an entity, and for that reason it is not deemed to be a critical problem.

\subsection*{P4 - Move Entities Behind Another Entity}
To move a entity behind another entity was a problem for one of the testees, since the testee was unable to understand where the button to do this were.
When told which button pushed an entity back, the testee felt that the icon was not understandable.
Furthermore, the testee though that the button would push an entity in front of another instead of behind an entity.
Therefore, the testee neede help to figure out how to use this functionality.
Since the testee had so many problems with this problem it is deemed as a serious problem.

\subsection*{P5 - Swap Colours}
The button to swap colours was deemed by the testees to not be understandable.
Furthermore none of the testees did figure out how the button worked even after getting told how it worked.
For that reason this problem is a critical problem, and should be fixed in the next sprint of \textit{Piktotegner}.

\subsection*{P6 - Add Search Word}
The problem occurred when one of the testees should add a search word to the search word list.
The testee did, however, only need a little help to figure out how to add the word to the list.
As only one of the testees were not able to add it to the list and just had few problems doing this, the problem is deemed to be a cosmetic problem.

\subsection*{P7 - Delete Entity}
When deleting an entity the user have to select the selection tool and then select the entity that have to be removed.
However, none of the testees understood that they had to select the selection tool to do this.
Both of the testees though that there would be an eraser to remove entities.
Furthermore, both of the testees tried to double press the entity because they though that would select the entity.
However, after few seconds and a bit help they were both able to see that selecting an entity would allow them to delete it.
Therefore is the problem deemed to be a serious problem. 

\subsection*{P8 - Colour Picker}
Only one of the testees had a problem with the colour picker.
The problem was that the testee though that pressing the button that pick the last picked colour would open the colour picker.
However, after several seconds the testee figured out that pressing the colour picker would lead them to picking the colour.
Since only one of the testee had a little problem with the problem, it is deemed to be a cosmetic problem.

\subsection*{P9 - Play Sound}
To play the sound of a pictogram the user have to go into the recording dialogue, which happens by pressing the record button.
The testees did not deem this understandable as the record button should only be for recording sound.
However, the testees did after few seconds figure out that the record dialogue would be able to play the sound of a pictogram, which is why the problem is a cosmetic problem.
%Suggested solutions